### 2022-03-11 paper/paper.tex
Clarify Higgs boson lifetime

% BEGIN HEADER CONFIGURATION
%--------------------------------------------%
\usepackage{fancyhdr, extramarks}
\pagestyle{fancy}

@@

\subsection{Collision and Detection}
Most protons in opposing beams zoom past each other without appreciable interaction.
Rarely, however, two protons collide head-on, setting in motion a chain of interactions which ultimately produces a cascade of familiar elementary particles such as electrons, protons, neutrons, muons, photons, and neutrinos.
These secondary particles are collectively called the collision's \textit{decay signature}, and fly outward in all directions from the primary collision point through a surrounding particle detector.
This brings us to a key concept:
\begin{quote}
    The exotic particles of interest in high-energy physics (e.g. a Higgs boson) decay far, far before they can interact with the detector.
    The detector measures only the secondary particles further down the decay chain.
\end{quote}
In other words, \textit{we have no way of detecting a Higgs boson directly.
The best we can do is infer its presence from the nature of the collision's decay signature}.
Thus, to progress, we need a quantitative description of a decay signature.

>>>>

% BEGIN HEADER CONFIGURATION
%--------------------------------------------%
\setlength{\headheight}{13.6pt}
\usepackage{fancyhdr, extramarks}
\pagestyle{fancy}

@@

\subsection{Collision and Detection}
Most protons in opposing beams zoom past each other without appreciable interaction.
Rarely, however, two protons collide head-on, setting in motion a chain of interactions which ultimately produces a cascade of familiar elementary particles such as electrons, protons, neutrons, muons, photons, and neutrinos.
These secondary particles are collectively called the collision's \textit{decay signature}, and fly outward in all directions from the primary collision point through a surrounding particle detector.
This brings us to a key concept:
\begin{quote}
    The exotic particles of interest in high-energy physics decay far, far before they can interact with the detector (for example, a Higgs boson has a mean lifetime of the order $ \SI[print-unity-mantissa = false]{e-22}{\second} $).
    The detector measures only the secondary particles further down the decay chain.
\end{quote}
In other words, \textit{we have no way of detecting a Higgs boson directly.
The best we can do is infer its presence from the nature of the collision's decay signature}.
Thus, to progress, we need a quantitative description of a decay signature.
